---
title: "Bioinformatics exercise of section 4"
author: "Kingsley"
date: "22/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## question 1

creating a function that calculates the cube root for a number
```{r,func1}
cuberoot <- function(x) {
  x^3
}

cuberoot(21)

```

## question 2

use 'sapply' to calculate the cubed root for the numbers 44,77,99,123
```{r,sapply}
cuberoot <- function(x) {
  x^3
}
x <- c(44,77,99,123)
sapply(x,cuberoot)
```

## question 3

use `if` to test whether object `mtcars.tsv` exists and run `head` if it does exist.
```{r,cond1}
if (file.exists("mtcars.tsv")) {
  head(mtcars,file="mtcars.tsv",quote=FALSE,sep="\t")
}
```

## question 4

Use `apply` to get the maximum value in each column of mtcars.
```{r,apply}
mtcars_colnames <- colnames(mtcars)
mtcars_colnames
```

finding the maximum value in each column of mtcars
```{r,apply2}
mv <- function(x) {
  max<- max.col(x)
}
mv(mtcars$mpg)
mv
apply(mtcars,2,max)
```

## question 5

Use `replicate` to quantify how frequent it is to draw the same number three times where the pool of numbers consists of 0 to 9.
```{r,replicate}
cointoss<-function(){
    sample(c(0,9),3,replace=TRUE)
}
res <- replicate(3,cointoss())
res
```

```{r,sessioninfo}
sessionInfo()
```