---
title: "Bioinfomatics exercise of practice 2"
author: "Kingsley"
date: "10/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Session 2

## Checking my understanding 

solving the questions below.

1. Create a scatterplot of mtcars weight (x axis) versus mpg (y axis). 
Include x and y axis labels and a main heading.

2. Sort mtcars by weight (wt) and create a horizontal barplot of wt values so heaviest ones at shown at the top of the bar plot.
The plot should be labeled so it is clear to see which bar belong to which car.
Include an axis label and main title.

3. Create a box plot of iris petal lengths.
Each species should be a different category.
Chart needs axis labels and a main title.

```{r, question1}
mtcars[,c("wt","mpg")]
mylm <- lm(mtcars$wt ~ mtcars$mpg)
plot(mtcars$wt,mtcars$mpg, 
     xlab="weight",
     ylab="mpg",
     main="Mtcars weight and mpg",
     pch=19)
```

```{r, question2}
mycars <- mtcars[order(mtcars$wt),]
par(mar=c(5,12,5,3))
barplot(mycars$wt, xlim= c(0,6), horiz=TRUE,las=1,names.arg=rownames(mycars),cex.names=0.6,main="mtcars weights",xlab="car weight (lb/1000)")
grid()
```


```{r, question3}
setosa <- subset(iris,Species=="setosa")
head(setosa)
virginica <- subset(iris,Species=="virginica")
head(virginica)
versicolor <- subset(iris,Species=="versicolor")
head(versicolor)
boxplot(list(setosa$Petal.Length,virginica$Petal.Length,versicolor$Petal.Length),names=c("Setosa","Virginica","Versicolor"),ylab="cm",main="Petal length")
```


## Checking my skills

For the TSV file located here: https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/mydata.tsv do the following:

1. Read it in and show the first 6 rows of data. 

2. Calculate the column and row means.

3. Use the `cor()` command to find the correlation coefficients between the 3 data sets. Which two datasets are the most similar?

4. Make a pairs plot of the three datasets.

## Answers to TSV file

```{r, tsv1}
URL="https://raw.githubusercontent.com/markziemann/SLE712_files/master/assessment_task3/bioinfo_asst3_part1_files/mydata.tsv"
x <- read.table(URL,header=TRUE,row.names = 1)
head(x)
```

```{r,tsv2}
colMeans(x)
rowMeans(x)
```

```{r,tsv3}
cor(x)
library("gplots")
heatmap.2(cor(x),trace="none",scale="none",margins = c(15,15))
```

```{r,tsv4}
pairs(x)
```


```{r,sessioninfo}
sessionInfo()
```

