---
title: "Bioinfomatics exercise of practice 1"
author: "Kingsley"
date: "10/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework questions for group study

1. calculate the sum of all integers numbers between 500 and 600

2. calculate the sum of all the square roots of all integers between 900 and 1000

3. Create the following datasets and plot a boxplot:

  a. A Sample 10000 datapoints from a normal distribution with mean of 50 and SD of 5
  
  b. A Sample 10000 datapoints from a normal distribution with mean of 50 and SD of 10 

4. Plot a and b above as a scatterplot, and plot the trend line.

5. Plot a and b above as histograms on the same chart.


## Question 1, calculating the sum of all integers numbers between 500 and 600
```{r, math1}
a <- c(500:600)
a
as.integer(a)
sum(a)
```

## Question 2, calculating the sum of all the square roots of all intergers between 900 and 1000
```{r, math2}
x <- c(900:1000)
x
as.integer(x)
sqrt(x)
sum(sqrt(x))
```

## Question 3a, create a sample of 1000 datapoints from a normal distribution with mean of 50 and SD of 5 and then plot a boxplot
```{r, math3a}
d <- rnorm(n = 1000, mean = 50, sd = 5)
d

## Question 3b, create a sample of 1000 datapoints from a normal distribution with mean of 50 and SD of 10 and then plot a boxplot

b <- rnorm(n = 1000, mean = 50, sd = 10)
b

boxplot(d,b,names=c("d","b"))
```


## Including Plots

```{r,q1-4}
mylm <- lm(b~d)
plot(d,b)
abline(mylm,col="red")
```

Plotting a and b above on same histogram charts
```{r,histograms1}

par(mfrow = c(2, 1))
hist(d,main="")
hist(b,main="")
```

```{r,sessioninfo}
sessionInfo()
```
