---
title: "Bioinformatics exercise 3 on Plant growth datasets"
author: "Kingsley"
date: "22/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing the built-in plant growth

loading and previewing the data frame, ensure proper loading and better idea of structure of the dataset

```{r, chunk1}
data("PlantGrowth")
head(PlantGrowth)
str(PlantGrowth)
```

## Calculating the numerical mean, median and interquartile ranges of the three groups of samples.


```{r,chunk2}
names(PlantGrowth) <- c("Weight(lbs)","Group_Name")
names(PlantGrowth)
unique(PlantGrowth$Group_Name)
```

looking up and renaming the different group codes to something more detailed.
```{r,chunk3}
lookup_Groupname <- c(ctrl="control condition", trt1 ="treatment condition_1",
                      trt2="treatment condition_2")
lookup_Groupname[c("ctrl","trt1","trt1")]
lookup_Groupname[PlantGrowth$Group_Name]
PlantGrowth[,3] <- unname(lookup_Groupname[PlantGrowth$Group_Name])
PlantGrowth[,3]
```

Analyzing the numerical mean, median and interquartile ranges of all groups.
```{r, chunk4}
summary(PlantGrowth)
```

comparing the box plots of the 3 groups
```{r,plots}
boxplot(`Weight(lbs)`~ Group_Name,  data = PlantGrowth )
```

```{r,sessioninfo}
sessionInfo()
```




